\documentclass[12pt, a4paper]{article}
\usepackage{import}

\import{../../lib/}{bridge.sty}

\title{\vspace*{-3.0cm}6\spades - A subtle hint}
\author{Bartek Słupik}
\begin{document}
\maketitle

After an auction I'd rather not waste your time on, East leads \xclubs2 against 6\spades.
\begin{enumerate}
    \item Find a double-dummy line of play to "win" the contract if the defence sleeps
    \item Find a defensive play to beat the contract
    \item Decide if it's possible to find it looking at just East's cards
\end{enumerate}

\handdiagramv
        {\vhand{AK7}{KT84}{AQT}{A87}}
        {\vhand{T5}{J765}{J8653}{92}}
        {\vhand{J9832}{Q}{K72}{QJ64}}
        {\vhand{Q64}{A932}{94}{KT53}}
        {}

\pagebreak

Assuming we lose no spade tricks, there is still a club loser to cater for. A round suit squeeze
against West would be possible, if he held the \xhearts J. We start by cashing three spades
and play a low heart towards the \xhearts Q. West wins, yawns, and returns a diamond.
That is a good start. 

We win the \xdiams A and cash the \xhearts K. Then we play the \xhearts T and watch East carefully.
He correctly covers with the Jack and we ruff. Great! Now, the heart threat is the \xhearts 9. If W holds it, 
he is soon to be squeezed just as we planned! We cash the remaining spades, and the \xdiams K, reaching the following position: 

\handdiagramv
        {\vhand{-}{8}{Q}{8}}
        {\vhand{-}{7}{J}{9}}
        {\vhand{-}{-}{7}{Q6}}
        {\vhand{-}{9}{}{T5}}
        {}

Upon leading the \xdiams 7 to the \xdiams Q, West must let go of one of the guards.

This is called a Guard Transfer Play - it enables us to seemingly waste a high card in order
for a lower guard to arise in a squeeze suit. If the other opponent holds it, the squeeze is going to operate.

If East does not cover with the \xhearts J, nor does he show any behavior suggesting the posession of the honor,
you should ruff the \xhearts T and proceed to play for West to have \xhearts AJ9x.

This enticing squeeze is far from working though, as the defence posesses an even more beautiful resource.
East, having seen the declarer pop in with the \xclubs J knows, that his partner posesses the \xclubs T.
Therefore, when declarer plays a low heart, he should signal for a club return with the \xhearts 5!
This cuts the dummy entries necessary for the squeeze and the contract has no more play.


\end{document}