\documentclass[12pt, a4paper]{article}
\usepackage{../../lib/bridgetex2}
\usepackage{polyglossia}
\usepackage{graphicx}
\usepackage{enumitem}
\setmainlanguage{english}

\title{Reverses}
\author{Krystyna Gasińska\\\small{based on Gavin Wolpert's class}}
\begin{document}
\maketitle

%%% PRIORITY: 100
%%% TITLE: Reverses, jump shifts and jump reverses
%%% SYSTEM BEGIN %%%

\subsubsection*{1\anysuit{x}\ -- 1\anysuit{y}\ -- ?}
\begin{itemize}
    \item 2\anysuit{z}, \anysuit{y}\ < \anysuit{z}\ = reverse
    \item 3\anysuit{y}, \anysuit{y}\ > \anysuit{z}\ = jump shift
    \item 3\anysuit{z}, \anysuit{y}\ < \anysuit{z}\ = jump reverse
\end{itemize}

\subsubsection*{1\mins\ -- 1\hearts\ -- ?}
\begin{itemize}
    \item 1\spades\ = 4\spades, 12-17
    \item 2\spades\ = 4\spades, (18)19+
\end{itemize}

%%% SYSTEM END %%%

\section{Reverse}
\begin{itemize}
    \item \fonce
    \item (16)17+ 4-5 distribution
    \item first suit always longer (with 5-5 we open higher suit)
    \item do not jump above a reverse to show extra values
    \item jump rebid of a minor denies 4\majs\ \vimp
\end{itemize}

\section{Jump shift}
\begin{itemize}
    \item \gf
    \item (18)19+
\end{itemize}

\section{Jump reverse}
\begin{itemize}
    \item \gf
    \item shows 6+ cards in first suit
    \item does not promise anything in the second suit
\end{itemize}

% note: it is not necessarily a good idea to google 'latex transparent'

\section{Reverse: responder's rebid}
\begin{itemize}
    \item Cheaper from $4^{\text{th}}$ suit and 2\nt\ = slow down bid ($\leq 7$pc), we are not in \gf.
    \item Bid above slow down bid = \gf.
    \item Bid below slow down bid = \fonce.
    \item After slow down bid responder may sign off in any of the opener's suits.
    \item Whatever responder bypass is denied. \vimp
    \item Bidding $4^{\text{th}}$ suit if it is above 2\nt\ shows 5-5 in responder's suits.
\end{itemize}

\section{Reacting to slow down}
\begin{itemize}
    \item After slow down bid opener is requested to bid 3 of the suit they opened or, if there is room
    below this bid, they can bid 2\nt\ or support for the responder's suit. All those bids are \nf.
\end{itemize}

\subsubsection*{Examples: opener's hand}

\begin{enumerate}
    \item
        \cihandp{9}{AK82}{A42}{KQJ75}{17}
        Just in place for a reverse. Open 1\clubs\ and reverse 2\hearts.
    \item
        \cihandp{K7}{AQ32}{AQJT96}{3}{16}
        Open 1\diams\ and rebid 2\hearts. Remember that jump rebid of a minor 
        denies 4\majs.
    \item 
        \cihandp{7}{AQT42}{2}{AKQT63}{15}
        Open 1\clubs, rebid 2\hearts\ and then bid again to show 5th \hearts.
    \item 
        You open 1\diams. Partner rebids 1\spades. \\
        \cihandp{J4}{AQT2}{AJ983}{AQ}{18}
        The hand is strong enough to reverse, but
        it is better to bid 2\nt\ showing balanced hand. We have two club stoppers. If we had no
        club stopper, we would reverse.
    \item 
        \cihandp{5}{A4}{KJ863}{AKQ63}{17}
        This hand is not strong enough to jump shift. Open 1\diams\ and rebid 2\clubs.
    \item
        You open 1\clubs. Partner rebids 1\spades. \\
        \cihandp{4}{42}{AK2}{AKQ9732}{16}
        Jump reverse to 3\diams\ single suited \clubs\ hand and \gf.
        
\end{enumerate}

\subsubsection*{Examples: responder's hand}
\begin{enumerate}
    \item
        Partner opened 1\diams, you bid 1\spades, partner rebid 2\hearts. \\
        \cihandp{KQ65}{T2}{QJ4}{A642}{12}
        Bid 3\diams\ showing support for \diams. It is a \gf\ bid.
    \item
        Partner opened 1\diams, you bid 1\spades, partner rebid 2\hearts. \\
        \cihandp{K765}{T2}{Q84}{J642}{6}
        Bid 2\nt\ -- \textbf{slow down}.
\end{enumerate}

\end{document}
