\documentclass[12pt, a4paper]{article}
\usepackage{import}

\import{../../lib/}{bridge.sty}

\begin{document}

\handdiagramh{\hhand{KQ963}{843}{32}{A85}}{9}
        {}{}
        {\hhand{A4}{AKJT92}{KT4}{QJ}}{18}
        {}{}
        {}

\begin{center}
    \begin{tabular}{cccc}
        \nvul{W} & \nvul{N} & \nvul {E} & \nvul{S} \\
        -- & -- & \pass & 1\hearts \\
        \pass & 2\hearts & \pass & 4\hearts \\
        \multicolumn{4}{l}{all pass}
    \end{tabular}
\end{center}

Lead: 9\clubs.
\begin{center}
    ***
\end{center}
The correct play is to draw one trump (both opponents
follow) and then
take care of spades (throw a club on Q\spades).
If spades are no worse then 2-6, we will lose 
2 diamonds and one trump. Even if opponents
ruff the third spade (we still throw away the club,
unless it is a Q\hearts, in which case we overruff),
they will (probably$^*$) have no possibility to use the last trump.

\vspace{0.2cm}

\noindent
$*$ There is are slight chance that the lead was a singleton and
opponents can now ruff (or overruff) the club,
but that would mean that E started with:
\chandp{J5}{65}{J5}{KT96432}{5}

\noindent
and in that case he would probably open 3\clubs (or
we are truly unlucky).

The second case is that E started with 3 trumps and 
a singleton diamond, but we counted 2 diamond losers 
anyway, so it does not matter if one of the diamonds
ends up ruffed. 

\vspace{0.2cm}

And what will happen if we decide to draw 2 trumps
at the beginning? W follows only once, throwing out
6\diams. If the third spade gets ruffed, E will play
a trump, and we will have no more trumps in dummy to
ruff a third diamond. But that is not the case here.
W turns out to have only 2 spades, so we throw away the
club on Q\spades. And what now? We have to try finesse
A\diams. We play 2\diams, E follows with 5\diams, 
W takes the king with ace, and plays a diamond
to E's jack or queen, E plays a Q\hearts and we lost the contract.
But what if we put T\diams instead of king? If ace is
with E we will win anyway, if not, there is still 
chance W has AQ\diams. He takes ten with the queen, and
has no communication to partner, he must play a club,
which we ruff and play K\diams. W takes it with ace and
plays a club again, we also ruff it and now we can ruff
our third diamond (it does not matter if E overruffs, 
Q\hearts will win a trick anyway).

Of course, if E would play jack to our 2\diams, we would
play king.

\vspace{0.2cm}

Both lines of play work out if A\diams is with E.
Both lose, if spades are worse then 2-4 and hearts worse then 2-2. Both wins
with the distribution as below. However, the first one
wins also with Q\diams being with E, while W loses.
So is there any distribution where the second play
is superior? Yes, if hearts are 2-2 and spades are 5-1.
However it is less possible then the Q\diams being with E.

\vspace{0.2cm}

The complete hand was:

\handdiagramh{\hhand{KQ963}{843}{32}{A85}}{9}
        {\hhand{JT75}{Q65}{J5}{K643}}{7}
        {\hhand{A4}{AKJT92}{KT4}{QJ}}{18}
        {\hhand{82}{7}{AQ9876}{T972}}{6}
        {}



\end{document}