\documentclass[12pt, a4paper]{article}
\usepackage{import}

\import{../../lib/}{bridge.sty}

\begin{document}

After the concise bidding: 

\begin{center}
\begin{tabular}{cccc}
    \vul{W} & \nvul{N} & \vul {E} & \nvul{S} \\
    1\hearts & \pass & \pass & 4\spades \\
    \pass & \pass & \pass & \pass 
\end{tabular}
\end{center}

\noindent
you find your dummy with:

\handdiagramh{\hhand{J7}{872}{KJ82}{QT63}}{7}{}{}{\hhand{AKQ9863}{J5}{7}{AJ7}}{15}{}{}{WE}

Lead: K\hearts, E takes with A\hearts and plays 4\hearts to ours J\hearts and W's Q\hearts. \\
W continues with T\hearts, E shows out (5\clubs) and you ruff. What do you do next?
\begin{center}
    ***
\end{center}

In addition to the two \hearts losers, we see two more: \clubs and \diams.
The right opponent, who passed their partner's opening bid, already came out with 4 points.
It looks like he doesn't have even a queen more. Therefore, there is no point in finessing the K\clubs.
There is also no chance to cash all trumps in order to endplay W: he will be left with 
\hhand{--}{x}{A}{Kx} and will be able to go out with a \hearts. The only successful line of play is
to hope that W has at most one trump. We can cash A\spades and lead a \diams towards the K\diams.
If W ducks we can put down the K\diams, securing the contract. If he takes the \diams with an ace, he
is endplayed. Playing \hearts allows us to throw \clubs loser away. Playing club will also take away
one of our \clubs loser. If W plays \diams we can take with J\diams (Q\diams is also with W).
We can later throw away our second \clubs loser on K\diams.

\handdiagramh{\hhand{J7}{872}{KJ82}{QT63}}{7}{\hhand{T52}{A4}{T953}{9852}}{4}{\hhand{AKQ9863}{J5}{7}{AJ7}}{15}{\hhand{4}{KQT963}{AQ64}{K4}}{14}{WE}

\noindent
Why this play doesn't work if W has more trumps?

\vspace{0.5cm}

\noindent
Do you see how \textbf{each} opponent could defeat the contract?

\end{document}