\documentclass[12pt, a4paper]{article}
\usepackage{import}

\import{../../lib/}{bridge.sty}

\begin{document}


\handdiagramh{\hhand{QJ6}{J93}{A7}{AJ653}}{13}
        {}{}
        {\hhand{74}{KT}{KQT542}{K82}}{11}
        {}{}
        {}

\begin{center}
\begin{tabular}{cccc}
        \nvul{W} & \nvul{N} & \nvul {E} & \nvul{S} \\
        --       & --      & \pass     & 1\diams \\
        2\diams  & 3\clubs & \pass     & 3\diams \\
        \pass    & 3\spades & 3\nt     & \multicolumn{1}{l}{all pass}
\end{tabular}
\end{center}

Lead: 5\spades, E takes with the king and plays 6\hearts.
W takes with the queen and plays A\spades and 8\spades
(E follows with 9\spades and 3\spades).
We take the third spade with Q\spades. What do you do next?
\begin{center}
    ***
\end{center}

By the left opponent Michaels bid, we know that he 
started with 5 spades and 5 hearts. If he also has 3\clubs,
it means that we can take at most 4 diamond (as they are
divided 0-5), but we can also try to finesse Q\clubs
and take 4 more tricks in that suit (if finesse wins).
If, on the other hand, diamonds are divided
no worse than 1-4, we can take all 6 diamonds (finessing
the jack) and 2 top clubs. However, if diamonds are
divided 2-3 or 3-2, we shouldn't finesse the jack, but start
with cashing the top diamonds instead. Can we find out
what the actual distribution is, before it is too late?
Yes. We should play the A\diams first. If diamonds are
0-5 we will know immediately, and still be able to collect
3 more diamonds (finessing J\diams). If both opponents follow,
we can cash two top clubs first, before handling the diamonds.
This play will give us the full information about W's hand:
if he follows twice, diamonds are 1-4, if he shows out to the
second club, the diamonds were 2-3, and if he shows out to the first
club already, then the diamonds are 3-2. This way we can play
the minor suits with certainty.

\vspace{0.3cm}

The actual distribution was:

\handdiagramh{\hhand{QJ6}{J93}{A7}{AJ653}}{13}
        {\hhand{K93}{864}{J983}{QT7}}{6}
        {\hhand{74}{KT}{KQT542}{K82}}{11}
        {\hhand{AT852}{AQ752}{6}{94}}{10}
        {}

\end{document}